Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-22 docs/Truman/LocalConservation/paper/paper.tex
Added discussion of coarse results

\section{Conclusions}
We've developed a locally conservative formulation of DPG by leveraging
Lagrange multipliers. While the formulation is provably convergent and robust, it does
increase the number of unkowns in the system and changes the structure from
symmetric positive-definite to a saddlepoint problem. Numerical results
indicate that the method delivers what it promises with local flux imbalances
hovering close to machine precision, but they also indicate that for most of the
problems considered, standard DPG is close to conservative and becomes more so
with refinements. For the Stokes problems, standard DPG suffered similar mass
loss as standard least squares on coarse meshes, but made up the lost mass with further
resolution.
Probably the most encouraging result of these experiments is
that enforcing local conservation did not change the nature of the solutions
too significantly. Standard DPG has a lot of attractive features, and we wish
to preserve those.

>>>>

The most significant benefit of enforcing local conservation for these
problems is that it allows us to recover the essential flow features with much
coarser meshes. On the $r=0.6$ cylinder problem, the peak velocity magnitude
of the conservative solution is fairly close on the coarsest mesh, while the
nonconservative solution severely underpredicts the peak. With the $r=0.9$
cylinder, this problem is only exacerbated. After just one adaptive
refinement, the conservative solution nails the peak velocity. The
nonconservative solution is completely useless at this point. We see the same
thing with the backward facing step problem. The conservative solution is
great on the coarsest mesh, while standard DPG needs a lot more resolution
before it even starts to look right.

\section{Conclusions}
We've developed a locally conservative formulation of DPG by leveraging
Lagrange multipliers. While the formulation is provably convergent and robust, it does
increase the number of unkowns in the system and changes the structure from
symmetric positive-definite to a saddlepoint problem. Numerical results
indicate that the method delivers what it promises with local flux imbalances
hovering close to machine precision, but they also indicate that for most of the
problems considered, standard DPG is close to conservative and becomes more so
with refinements. For the Stokes problems, standard DPG suffered similar mass
loss as standard least squares on coarse meshes, but made up the lost mass with further
resolution. On problems where local conservation was really stressed,
restricted DPG was able to deliver reasonable solutions with much less
resolution than standard DPG.
Probably the most encouraging result of these experiments is
that enforcing local conservation did not change the nature of the solutions
too significantly. Standard DPG has a lot of attractive features, and we wish
to preserve those.
